---
title: "Using LUBRIDATE: For Time & Date in R"
author: "Uma Negi"
date: '2022-04-19'
output:
  html_document: default
  pdf_document: default

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Here we will see what packages of R are used to represent the Date and Time Data Type in R. So we will install and see some example

Installing LUBRIDATE Package which deals with Date and Time in R

##### Loading the Lubridate Package
```{r}
library(lubridate)
```

##### Using Today and Now function of Lubridate to know Today's Date and present Time
```{r}
today()                                  #shows today's date (Y-M-D)
now()                                    #shows today time & date (Y-M-D H:M:S)
```

##### Converting from strings  to date format (YYYY-MM-DD)
```{r}
ymd("2022-04-19")
mdy("April 19th, 2022")
dmy("04-April-2022")
ymd(20220419)
```

##### Creating Date-Time Components
```{r}
ymd_hms("2021-01-20 20:11:59")
mdy_hm("01/20/2021 08:01")

```

##### Switching between existing Date-Time objects 
```{r}
as_date(now())           
as_date("2021-01-20 08:01:00")           #only shows date component
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.





